Ultrafast Electron Microscopes: Design Criteria, Electron Sources, and Column Modeling

### 2013-04-12 inc/extension/implementation/implementation.tex
finished including andreas comments on extension chapter
citations are now preceeded by non-breaking space (~)
massive spellchecking

%The model presented in this chapter is deceptively hard to implement.
%As noted by Michalik and Sipe in their original paper \cite{michalik_analytic_2006}, in the absence of space-charge, the solution of the system of equations in \ref{eq:ag_original} may be solved analytically and result in the standard equations of Gaussian optics.
%With the inclusion of space-charge (that is the inclusion of electron-electron repulsion) the system must be solved by numerical methods.
%The scaling of the terms requires special consideration of error-handling.

@@

Recently the model was rewritten in Perl, and is called \verb!Physics::UEMColumn!.
Perl is a dynamic scripting language known for its versitility and flexibility.
In this implementation, the model is implemented as a decoupled set of high-level object-oriented classes.

\verb!Physics::UEMColumn! has been released as open source software under the terms of the Artistic License (a derivative of the GNU General Public License), which allows for free use of the software.
The current state of development of the simulation toolkit is publically available at \url{https://github.com/jberger/Physics-UEMColumn}.
Releases of the toolkit are available via the Comprehensive Perl Archive Network (CPAN), which is a central repository of software developed for Perl, a standard tool for the language.
The CPAN has several tracker sites, see for example \url{https://metacpan.org/module/Physics::UEMColumn}.

A simulation script is composed of creating instances of the classes that represent the column, the pulse, electron-optical elements like magnetic lenses and RF cavities.
These objects act as containers for the information about the physical object that they represent.
Further they manage progammatic tasks related to those objects.
For example, electron-optical element objects manage the Gaussian region-of-influence (\ref{eq:reg_of_influence}) and calculate the force that their fields apply to the pulse.
This allows for clean, managable and extensible code.

@@

Many scripts which use \verb!Physics::UEMColumn! were need to generate data used in the writing of this paper.
I have included most of them in the source repository which is available at \url{https://github.com/jberger/Thesis}.

Additionally, a development version of the bin model presented in Section \ref{sec:bin_model} is available at \url{https://github.com/jberger/Physics-Photoemission}.
Once I am sufficently confident in its implementation, and more importantly its voracity, I intend to release it to the CPAN as well, most likely under the name \verb!Physics::Photoemission!.
This module depends on the much larger Perl project PDL (\url{http://pdl.perl.org}), a matrix-oriented numerical library, making it slightly more difficult to install, however the speed and implementational simplicy benefit added by that dependency is marked.

@@

>>>>

%The model presented in this chapter is deceptively hard to implement.
%As noted by Michalik and Sipe in their original paper~\cite{michalik_analytic_2006}, in the absence of space-charge, the solution of the system of equations in \ref{eq:ag_original} may be solved analytically and result in the standard equations of Gaussian optics.
%With the inclusion of space-charge (that is the inclusion of electron-electron repulsion) the system must be solved by numerical methods.
%The scaling of the terms requires special consideration of error-handling.

@@

Recently the model was rewritten in Perl, and is called \verb!Physics::UEMColumn!.
Perl is a dynamic scripting language known for its versatility and flexibility.
In this implementation, the model is implemented as a decoupled set of high-level object-oriented classes.

\verb!Physics::UEMColumn! has been released as open source software under the terms of the Artistic License (a derivative of the GNU General Public License), which allows for free use of the software.
The current state of development of the simulation toolkit is publicly available at \url{https://github.com/jberger/Physics-UEMColumn}.
Releases of the toolkit are available via the Comprehensive Perl Archive Network (CPAN), which is a central repository of software developed for Perl, a standard tool for the language.
The CPAN has several tracker sites, see for example \url{https://metacpan.org/module/Physics::UEMColumn}.

A simulation script is composed of creating instances of the classes that represent the column, the pulse, electron-optical elements like magnetic lenses and RF cavities.
These objects act as containers for the information about the physical object that they represent.
Further they manage programmatic tasks related to those objects.
For example, electron-optical element objects manage the Gaussian region-of-influence (\ref{eq:reg_of_influence}) and calculate the force that their fields apply to the pulse.
This allows for clean, manageable and extensible code.

@@

Many scripts which use \verb!Physics::UEMColumn! were need to generate data used in the writing of this thesis.
I have included most of them in the source repository which is available at \url{https://github.com/jberger/Thesis}.

Additionally, a development version of the bin model presented in Section \ref{sec:bin_model} is available at \url{https://github.com/jberger/Physics-Photoemission}.
Once I am sufficiently confident in its implementation, and more importantly its voracity, I intend to release it to the CPAN as well, most likely under the name \verb!Physics::Photoemission!.
This module depends on the much larger Perl project PDL (\url{http://pdl.perl.org}), a matrix-oriented numerical library, making it slightly more difficult to install, however the speed and implementational simplicity benefit added by that dependency is marked.

@@

%TODO compare to luiten RF compressed pulse system as example (or might go in results section)

### 2013-04-12 inc/extension/initial_conditions/bin_model_figure.tex
massive spellchecking

\begin{figure}
  \centerline {
    \subfloat[][]{
      \label{fig:bin_model_acc}
      \begin{tikzpicture}
        \input{Acc}
      \end{tikzpicture}
    }
    \subfloat[][]{
      \label{fig:bin_model_vmax}
      \begin{tikzpicture}
        \input{Vmax}
      \end{tikzpicture}
    }
    \\
  }
  \centerline{
    \subfloat[][]{
      \label{fig:bin_model_equal}
      \begin{tikzpicture}
        \input{Equal}
      \end{tikzpicture}
    }
  }
  \caption[Results of bin model for computing initial conditions]{
    Comparison of the results of the bin model and AG model allowed functional forms for three different input parameters cases.
    Compared are: \subref{fig:bin_model_acc} the DC acceleration dominated case, \subref{fig:bin_model_vmax} the photoemission energy dominated case, and \subref{fig:bin_model_equal} an intermediate case.
    For the Gaussian spatial distribution whose variance is $\sigma_z$ (red) and the momemtum chirp $\gamma_z$ (green) the simulated data (solid) and the fit to the AG allowed form (dashed) are decently well matched in all cases.
    Unfortunately, the model only allows for a constant local momentum variance $\eta_z$ (green) and in all but the extreme acceleration dominated case \subref{fig:bin_model_acc} the model cannot well represent the simulated data.
  }
  \label{fig:bin_model}
\end{figure}

>>>>

\begin{figure}
  \centerline {
    \subfloat[][]{
      \label{fig:bin_model_acc}
      \begin{tikzpicture}
        \input{Acc}
      \end{tikzpicture}
    }
    \subfloat[][]{
      \label{fig:bin_model_vmax}
      \begin{tikzpicture}
        \input{Vmax}
      \end{tikzpicture}
    }
    \\
  }
  \centerline{
    \subfloat[][]{
      \label{fig:bin_model_equal}
      \begin{tikzpicture}
        \input{Equal}
      \end{tikzpicture}
    }
  }
  \caption[Results of bin model for computing initial conditions]{
    Comparison of the results of the bin model and AG model allowed functional forms for three different input parameters cases.
    Compared are: \subref{fig:bin_model_acc} the DC acceleration dominated case, \subref{fig:bin_model_vmax} the photoemission energy dominated case, and \subref{fig:bin_model_equal} an intermediate case.
    For the Gaussian spatial distribution whose variance is $\sigma_z$ (red) and the momentum chirp $\gamma_z$ (green) the simulated data (solid) and the fit to the AG allowed form (dashed) are decently well matched in all cases.
    Unfortunately, the model only allows for a constant local momentum variance $\eta_z$ (green) and in all but the extreme acceleration dominated case \subref{fig:bin_model_acc} the model cannot well represent the simulated data.
  }
  \label{fig:bin_model}
\end{figure}

### 2013-04-12 inc/extension/initial_conditions/initial_conditions.tex
massive spellchecking

The initial tranverse properties of the emitted electron beam are easily understood.
The electron pulse's initial spatial variance is simply
\begin{equation}
\sigma_{\smallT } ( 0 ) = ( \Delta x )^{2} = ( \Delta y)^{2} = \frac{ w^{2} }{ 2 } \punct{.}
\end{equation}
For spatially-uniform photoemission from a planar photocathode, from symmetry we have $ \gamma_{\smallT} ( 0 ) = 0 $; i.e., there is no initial transverse spatial momentum chirp across the electron bunch.
Finally, thanks to the careful analysis of Dowell and Schmerge~\cite{dowell_quantum_2009} (confirmed by Jensen \textit{et. al.}~\cite{jensen_emittance_2010}), we know that metallic photocathode's initial transverse momentum variance at $ t = 0 $ is given by
\begin{equation} \label{eq:jensen_eta}
  \eta_{ \smallT } ( 0 )  = (\Delta p_{\smallT})^2 \approx \frac{ m }{ 3 } ( \hbar \omega - \Phi ) \punct{,}
\end{equation}
in the limit where the maximum excess photoemission energy, $ \Delta E = \hbar \omega - \Phi $ is significantly greater than the thermal energy $ k_{B} T $ of the electrons in the photocathode -- a condition that is generally met in laser-driven DC photoelectron guns.
For completeness we note that for thermionic emission $\Delta p_{\smallT} = \sqrt{m k_B T_e}$ where $k_B$ is the Boltzmann constant and $T_e$ is the electron temperature~\cite{dowell_quantum_2009,jensen_emittance_2010}..

% longitudinal
In the longitudinal direction ($z$), the interplay between acceleration, $ a = e E_{DC}/m $, in the DC gun and the physics of the photoemission process determine the initial values of $\sigma_z$, the longitudinal spatial variance, and $\gamma_z$, the longitudinal momentum chirp, of an electron bunch.
Two limiting regimes for the initial longitudinal variances $ \sigma_{i} ( 0 ) $ are readily identified: (i) when the incident drive laser pulse duration is sufficently long to ensure that the distance the electrons travel due to acceleration in $ E_{DC} $ over the laser pulse duration is much greater than the distance traveled by electrons moving with a constant velocity $ v_{max} = \sqrt{ 2 \Delta E / m } $, the maximum photoemission velocity, over the same time period; and (ii) the opposite regime for sufficiently short laser pulse durations.

% dc dominated
In the long-pulse regime, the DC field dominated case, we assume that the intrinsic velocity of the emitted electrons is negligable.
The emitted electrons travel an average distance $ \Delta z $, during the $ \Delta t_{ L } $ rms laser pulse duration given by,
\begin{equation}
  \sqrt{ \sigma_{ z } ( 0 ) } \approx \Delta z = \frac{ 1 }{ 2 } a ( \Delta t_{L} )^{ 2 }  = \frac{ e E_{ DC } \tau^{ 2 } }{ 4 m } \punct{.}
\end{equation}
By a similar logic, we can say that the `front' of the pulse then has a velocity equal to $ a \Delta t_{ L } $, while the `back' of the pulse (a distance $ \frac{ 1 }{ 2 } \sqrt{ \sigma_{ z } ( 0 ) } $ from the electron bunch peak) has zero velocity since it has just been generated. From this one sees that the initial linear chirp across the pulse is given by 
\begin{equation}
  \gamma_{ z } ( 0 ) \approx \Delta v \Delta z = m a \Delta t_{ L } \sqrt{ \sigma_{ z } ( 0 ) } = \frac{ e E_{ DC } \tau }{ \sqrt{ 2 } }\sqrt{ \sigma_{ z } ( 0 ) } \punct{.}
\end{equation}

@@

This simulation repeats for each time slice until the finish time, at which point the laser has essentially stopped creating electrons.
At this time, the earliest fastest electrons will be a distance 
\begin{equation}
  z_{max} = v_{max}N \tau + \frac{e E_{ DC }}{2 m} (N \tau)^2 
\end{equation}
away from the the photocathode, and the the electrons created in the last slice will be at $z=0$.
By counting the electrons in each spatial bin and fitting to a gaussian, we can determine $\sigma_z(0)$, the inital longitudinal spatial variance of the pulse.
Taking a weighted average of the velocity of the electrons in each spatial bin and fitting to a linear function across the pulse (as defined by the AG model), we can determine the initial longitudinal velocity (momentum) chirp $\gamma_z(0)$.
As seen in \ref{fig:bin_model}, the shapes of the actual output compare well with the fitted functional form for both of these parameters for all reasonable ranges of field and laser pulse duration.

@@

Finally, the velocity uncertainty in each bin can be computed, however unlike the previous parameters, the AG model only allows for a constant value of $\eta_z(0)$, the local momentum variance across the pulse.
Unfortunately, \ref{fig:bin_model} clearly demonstrates that the local momentum variance is not constant over the inital photo-generated electron bunch; in fact it varies by almost an order of magnitude over the $ 1/e^{2} $ maximum full-width of the electron bunch. 
The narrowest momentum distribution are clearly at the front of the bunch where only the earliest generated electrons with initial velocity near $ v_{max} $ initially reside; the largest distribution is at the back where the last electrons generated still haven't had time to seperate from one another.

>>>>

The initial transverse properties of the emitted electron beam are easily understood.
The electron pulse's initial spatial variance is simply
\begin{equation}
\sigma_{\smallT } ( 0 ) = ( \Delta x )^{2} = ( \Delta y)^{2} = \frac{ w^{2} }{ 2 } \punct{.}
\end{equation}
For spatially-uniform photoemission from a planar photocathode, from symmetry we have $ \gamma_{\smallT} ( 0 ) = 0 $; i.e., there is no initial transverse spatial momentum chirp across the electron bunch.
Finally, thanks to the careful analysis of Dowell and Schmerge~\cite{dowell_quantum_2009} (confirmed by Jensen \textit{et. al.}~\cite{jensen_emittance_2010}), we know that metallic photocathode's initial transverse momentum variance at $ t = 0 $ is given by
\begin{equation} \label{eq:jensen_eta}
  \eta_{ \smallT } ( 0 )  = (\Delta p_{\smallT})^2 \approx \frac{ m }{ 3 } ( \hbar \omega - \Phi ) \punct{,}
\end{equation}
in the limit where the maximum excess photoemission energy, $ \Delta E = \hbar \omega - \Phi $ is significantly greater than the thermal energy $ k_{B} T $ of the electrons in the photocathode -- a condition that is generally met in laser-driven DC photoelectron guns.
For completeness we note that for thermionic emission $\Delta p_{\smallT} = \sqrt{m k_B T_e}$ where $k_B$ is the Boltzmann constant and $T_e$ is the electron temperature~\cite{dowell_quantum_2009,jensen_emittance_2010}..

% longitudinal
In the longitudinal direction ($z$), the interplay between acceleration, $ a = e E_{DC}/m $, in the DC gun and the physics of the photoemission process determine the initial values of $\sigma_z$, the longitudinal spatial variance, and $\gamma_z$, the longitudinal momentum chirp, of an electron bunch.
Two limiting regimes for the initial longitudinal variances $ \sigma_{i} ( 0 ) $ are readily identified: (i) when the incident drive laser pulse duration is sufficiently long to ensure that the distance the electrons travel due to acceleration in $ E_{DC} $ over the laser pulse duration is much greater than the distance traveled by electrons moving with a constant velocity $ v_{max} = \sqrt{ 2 \Delta E / m } $, the maximum photoemission velocity, over the same time period; and (ii) the opposite regime for sufficiently short laser pulse durations.

% dc dominated
In the long-pulse regime, the DC field dominated case, we assume that the intrinsic velocity of the emitted electrons is negligible.
The emitted electrons travel an average distance $ \Delta z $, during the $ \Delta t_{ L } $ rms laser pulse duration given by,
\begin{equation}
  \sqrt{ \sigma_{ z } ( 0 ) } \approx \Delta z = \frac{ 1 }{ 2 } a ( \Delta t_{L} )^{ 2 }  = \frac{ e E_{ DC } \tau^{ 2 } }{ 4 m } \punct{.}
\end{equation}
By a similar logic, we can say that the `front' of the pulse then has a velocity equal to $ a \Delta t_{ L } $, while the `back' of the pulse (a distance $ \frac{ 1 }{ 2 } \sqrt{ \sigma_{ z } ( 0 ) } $ from the electron bunch peak) has zero velocity since it has just been generated. From this one sees that the initial linear chirp across the pulse is given by 
\begin{equation}
  \gamma_{ z } ( 0 ) \approx \Delta v \Delta z = m a \Delta t_{ L } \sqrt{ \sigma_{ z } ( 0 ) } = \frac{ e E_{ DC } \tau }{ \sqrt{ 2 } }\sqrt{ \sigma_{ z } ( 0 ) } \punct{.}
\end{equation}

@@

This simulation repeats for each time slice until the finish time, at which point the laser has essentially stopped creating electrons.
At this time, the earliest fastest electrons will be a distance 
\begin{equation}
  z_{max} = v_{max}N \tau + \frac{e E_{ DC }}{2 m} (N \tau)^2 
\end{equation}
away from the the photocathode, and the the electrons created in the last slice will be at $z=0$.
By counting the electrons in each spatial bin and fitting to a Gaussian, we can determine $\sigma_z(0)$, the initial longitudinal spatial variance of the pulse.
Taking a weighted average of the velocity of the electrons in each spatial bin and fitting to a linear function across the pulse (as defined by the AG model), we can determine the initial longitudinal velocity (momentum) chirp $\gamma_z(0)$.
As seen in \ref{fig:bin_model}, the shapes of the actual output compare well with the fitted functional form for both of these parameters for all reasonable ranges of field and laser pulse duration.

@@

Finally, the velocity uncertainty in each bin can be computed, however unlike the previous parameters, the AG model only allows for a constant value of $\eta_z(0)$, the local momentum variance across the pulse.
Unfortunately, \ref{fig:bin_model} clearly demonstrates that the local momentum variance is not constant over the initial photo-generated electron bunch; in fact it varies by almost an order of magnitude over the $ 1/e^{2} $ maximum full-width of the electron bunch. 
The narrowest momentum distribution are clearly at the front of the bunch where only the earliest generated electrons with initial velocity near $ v_{max} $ initially reside; the largest distribution is at the back where the last electrons generated still haven't had time to separate from one another.

### 2013-04-12 inc/extension/introduction.tex
massive spellchecking

In Chapter \ref{chap:ms_model}, I have introduced the AG model, originally presented by Michalik and Sipe~\cite{michalik_analytic_2006}.
Although it is a very impressive model and a very useful starting point, because it cannot include the influence of external forces on the pulse dynamics, it does not provide the complete picture of the evolution of an electron pulse through an entire microscope column.
Futher, it does not contain a set of initial conditions which reflect a realistic photoemission process.

In the following chapter, I will derive a set of initial conditions which, though simplistic, should be sufficient to simulate single-photon photoemission from a metal, and which may additionally serve as a basis for future sets of initial conditions for other photoemission processes.
I will then present a model which builds on and extends the AG model to include the influence of external forces on pulses.
I will also include the mathematical representations of magnetic lenses, TM$_{010}$ RF cavities, and DC accelerators.
With these computational tools it is possible to form one model which has the ability to simulate a UEM column.
Indeed I have implemeted this model in the Perl programming language, in a form generic enough to easily model many different electron column configurations and yet is computationally fast enough to be used to design and optimize a column.

>>>>

In Chapter \ref{chap:ms_model}, I have introduced the AG model, originally presented by Michalik and Sipe~\cite{michalik_analytic_2006}.
Although it is a very impressive model and a very useful starting point, because it cannot include the influence of external forces on the pulse dynamics, it does not provide the complete picture of the evolution of an electron pulse through an entire microscope column.
Further, it does not contain a set of initial conditions which reflect a realistic photoemission process.

In the following chapter, I will derive a set of initial conditions which, though simplistic, should be sufficient to simulate single-photon photoemission from a metal, and which may additionally serve as a basis for future sets of initial conditions for other photoemission processes.
I will then present a model which builds on and extends the AG model to include the influence of external forces on pulses.
I will also include the mathematical representations of magnetic lenses, TM$_{010}$ RF cavities, and DC accelerators.
With these computational tools it is possible to form one model which has the ability to simulate a UEM column.
Indeed I have implemented this model in the Perl programming language, in a form generic enough to easily model many different electron column configurations and yet is computationally fast enough to be used to design and optimize a column.

### 2013-04-12 inc/extension/liouvilles_theorem/liouvilles_theorem.tex
massive spellchecking

We note that, in the transverse directions ($\smallT$), this is consistent with the definition of `coherent fluence' employed by Reed \textit{et al.}~\cite{reed_evolution_2009} for time-resolved electron microscopy and, of course, the trasverse spatial emittance of an electron beam~\cite{jensen_theoretical_2006,siwick_ultrafast_2002}.
Additionally, though the AG model explicitly satisfies Liouville's Theorem, there are cases where the pulse's phase space product may change in a realistic system.
This effect is called ``emittance growth'' and is most commonly seen in TEM as a result of aberations in lens systems~\cite{oshea_reversible_1998}.
As will be seen in Section \ref{extension_limitations}, the AG model will, of necessity, only consider perfect lenses.

>>>>

We note that, in the transverse directions ($\smallT$), this is consistent with the definition of `coherent fluence' employed by Reed \textit{et al.}~\cite{reed_evolution_2009} for time-resolved electron microscopy and, of course, the transverse spatial emittance of an electron beam~\cite{jensen_theoretical_2006,siwick_ultrafast_2002}.
Additionally, though the AG model explicitly satisfies Liouville's Theorem, there are cases where the pulse's phase space product may change in a realistic system.
This effect is called ``emittance growth'' and is most commonly seen in TEM as a result of aberrations in lens systems~\cite{oshea_reversible_1998}.
As will be seen in Section \ref{extension_limitations}, the AG model will, of necessity, only consider perfect lenses.

### 2013-04-12 inc/gun/gun_design.tex
massive spellchecking

The acceleration region of our prototype UEM system has several features which are unique in comparison to standard electron guns.
As discussed in Chapter \ref{chap:considerations}, notable requirements for a UEM electron gun include the need to handle a large photoemission area and yet to retain all of the electrons, it may not employ a pin-hole to selectively clean the electron beam.
These necessities lead to several additional criteria.
The system must first be able to accept the large laser spot size needed to generate the electron beam.
Then, in order to accomodate this large electron pulse, both the cathode Wehnelt and anode aperture must be similarly large; in fact, the beam size at the anode aperture will typically be larger than at the emission source due to transverse beam expansion during acceleration.
Also, care must be taken to ensure a relatively uniform electric field for acceleration of the pulse.
While in transit from the cathode to the anode, this large beam is more susceptable to non-uniformities in the electic field given that it will span a larger volume of the acceleration region than the thin beams used in conventional TEM.

@@

These requirements led to the fabrication of cathode/Wehnelt and anode pair based on the design of Togawa \textit{et al.}~\cite{togawa_ceb6_2007} (pictured in \ref{fig:togawa-pic}).
A schematic of this design, overlayed by a Finite Element Model (FEM) simulation of the electic field, is shown in \ref{fig:gun-field}.
The simulation was performed using \texttt{FreeFEM++}, a free finite element partial differential equation solver and meshing toolkit (\url{http://www.freefem.org/ff++/index.htm}).
The FEM simulation modeled the features of the anode and cathode, while emulating gap walls at infinity by placing a linear potential on gap edges at a large distance.
From the field equipotentials, it is clear that this design has a consistently flat electric field for large displacements off the central axis.
Since the shape of the field is scale independent, the schematic shows that the aperture width and laser acceptance concerns are easily satisfied for an appropriate choice of scale.

@@

  \caption[An example of a tanh form acceleration region for three different ``sharpness'' values]{
    An example of a tahn form acceleration region (overall length 6.35mm) for three different ``sharpness'' values, the same data as in \ref{fig:gun-sharpness}\subref{fig:field_on_axis}.
    The square data points represent the on-axis electric field data from FEM simulations.
  }
  \label{fig:field_on_axis_fem}
\end{figure}

\ref{fig:field_on_axis_fem} compares the FEM computed electric field to the form asserted for the AG model (\ref{eq:anode_tanh}) for several values of the sharpness parameter $s$; the lines are the same as in \ref{fig:gun-sharpness}\subref{fig:field_on_axis}.
As derived in Section \ref{sec:gun_model}, the change of electric field strength near the anode will cause some divergence of the electic field which, in turn, will cause a divergence of the beam.
Future work will include investigating the designs of Butler %TODO reference
which may be able to build in an intrinsic lensing to compensate for this effect.

>>>>

The acceleration region of our prototype UEM system has several features which are unique in comparison to standard electron guns.
As discussed in Chapter \ref{chap:considerations}, notable requirements for a UEM electron gun include the need to handle a large photoemission area and yet to retain all of the electrons, it may not employ a pin-hole to selectively clean the electron beam.
These necessities lead to several additional criteria.
The system must first be able to accept the large laser spot size needed to generate the electron beam.
Then, in order to accommodate this large electron pulse, both the cathode Wehnelt and anode aperture must be similarly large; in fact, the beam size at the anode aperture will typically be larger than at the emission source due to transverse beam expansion during acceleration.
Also, care must be taken to ensure a relatively uniform electric field for acceleration of the pulse.
While in transit from the cathode to the anode, this large beam is more susceptible to non-uniformities in the electric field given that it will span a larger volume of the acceleration region than the thin beams used in conventional TEM.

@@

These requirements led to the fabrication of cathode/Wehnelt and anode pair based on the design of Togawa \textit{et al.}~\cite{togawa_ceb6_2007} (pictured in \ref{fig:togawa-pic}).
A schematic of this design, overlaid by a Finite Element Model (FEM) simulation of the electric field, is shown in \ref{fig:gun-field}.
The simulation was performed using \texttt{FreeFEM++}, a free finite element partial differential equation solver and meshing toolkit (\url{http://www.freefem.org/ff++/index.htm}).
The FEM simulation modeled the features of the anode and cathode, while emulating gap walls at infinity by placing a linear potential on gap edges at a large distance.
From the field equipotentials, it is clear that this design has a consistently flat electric field for large displacements off the central axis.
Since the shape of the field is scale independent, the schematic shows that the aperture width and laser acceptance concerns are easily satisfied for an appropriate choice of scale.

@@

  \caption[An example of a tanh form acceleration region for three different ``sharpness'' values]{
    An example of a tanh form acceleration region (overall length 6.35mm) for three different ``sharpness'' values, the same data as in \ref{fig:gun-sharpness}\subref{fig:field_on_axis}.
    The square data points represent the on-axis electric field data from FEM simulations.
  }
  \label{fig:field_on_axis_fem}
\end{figure}

\ref{fig:field_on_axis_fem} compares the FEM computed electric field to the form asserted for the AG model (\ref{eq:anode_tanh}) for several values of the sharpness parameter $s$; the lines are the same as in \ref{fig:gun-sharpness}\subref{fig:field_on_axis}.
As derived in Section \ref{sec:gun_model}, the change of electric field strength near the anode will cause some divergence of the electric field which, in turn, will cause a divergence of the beam.
Future work will include investigating the designs of Butler %TODO reference
which may be able to build in an intrinsic lensing to compensate for this effect.

### 2013-04-12 inc/gun/gun_model.tex
massive spellchecking

In the acceleration region of a UEM column, a constant electric field is applied to the newly created electron pulse, increasing its velocity until it achieves its ultimate velocity just upon leaving the region at the anode aperture.
As seen in Section \ref{sec:const_force}, this constant electric field does not affect the intrapulse dynamics, however the distortion in the electric field near this aperture causes the anode itself to act as a negative transverse lens. %TODO reference
Additionally, the longitudinal electric field stregth sharply decreases near the anode.
As the front of the pulse sees this change before the back, this changing field also acts as a pulse compression element.

@@

To model the radial action (negative transverse lensing), we can expand the radial force $F_r$ for electrons that are a distance $r$ radially outward from the center of the pulse,
\begin{equation}
  F_r(r,z^{\prime}) \approx F_r(r,z^{\prime}) + \frac{\partial F_r}{\partial r^{\prime}} r \,\text{.}
\end{equation}
Without an analytic form for $F$, we can appeal to Gauss' law (in absense of external charge),
\begin{gather}
  \frac{\partial F_x}{\partial x^{\prime}} + \frac{\partial F_y}{\partial y^{\prime}} + \frac{\partial F_z}{\partial z^{\prime}} = 2 \frac{\partial F_{\smallT}}{\partial r^{\prime}} + \frac{\partial F_z}{\partial z^{\prime}} = 0 \\
  \Rightarrow \frac{\partial F_{\smallT}}{\partial r^{\prime}} = - \frac{1}{2} \frac{\partial F_z}{\partial z^{\prime}} \,\text{,}
\end{gather} 
to see that the transverse lens traverse lens strength $M_{\smallT}$ from the anode is simply,
\begin{equation}
  M_{\smallT} = -\frac{1}{2}\frac{\partial F_z}{\partial z^{\prime}} \, \text{.}
\end{equation}

We may choose to assume that the on-axis field is defined as a smoothed step down function
\begin{equation} \label{eq:anode_tanh}
  F_z(0,z^{\prime}) = \frac{eV}{2z^{\prime}_A} \left( 1 - \tanh \left( \frac{ z^{\prime} - z^{\prime}_A }{ z^{\prime}_A / s } \right) \right) \,\text{,}
\end{equation}
where $V$ is the accelerating potential, $z^{\prime}_A$ is the position of the anode (the cathode assumed to be at $z^{\prime} = 0$) and $s$ is a constant quantifying the ``sharpness'' of the fall-off of the electric field.
Indeed, this form is analgous to the super-Gaussian envalope (\ref{eq:reg_of_influence}), however it is open ended on the cathode side, which is necessary for the electrons to be accelerated away from the photocathode.
Given this form the ``lensing'' strengths are then
\begin{gather}
  M_{\smallT} = -\frac{eVs}{4z^{\prime 2}_A} \operatorname{sech}^2 \left( \frac{z^{\prime} - z^{\prime}_A }{ z^{\prime}_A / s } \right) \\
  M_z = \frac{eVs}{2z^{\prime 2}_A} \operatorname{sech}^2 \left( \frac{z^{\prime} - z^{\prime}_A }{ z^{\prime}_A / s } \right) \, \text{.}
\end{gather}
As with the RF cavity, one needs to include the on-axis force (\ref{eq:anode_tanh}) in the overall pulse propagation kinematics.

\begin{figure}
  \centerline{
    \subfloat[][]{
      \label{fig:field_on_axis}
      \begin{tikzpicture}
        \input{onaxis}
      \end{tikzpicture}
    }
    \subfloat[][]{
      \label{fig:tanh_sharpness}
      \input{sharpness}
    }
  }
  \caption[An example of a tanh form acceleration region for three different ``sharpness'' values]{
    An example of a tahn form acceleration region (overall length 6.35mm) for three different ``sharpness'' values.
    The colored electric fields in figure \protect\subref{fig:field_on_axis} correspond to the pulse width (solid) and length (dashed) in figure \protect\subref{fig:tanh_sharpness}.
    This form is compared to FEM simulated electric field data in \ref{fig:field_on_axis_fem}.
  }
  \label{fig:gun-sharpness}
\end{figure}

>>>>

In the acceleration region of a UEM column, a constant electric field is applied to the newly created electron pulse, increasing its velocity until it achieves its ultimate velocity just upon leaving the region at the anode aperture.
As seen in Section \ref{sec:const_force}, this constant electric field does not affect the intrapulse dynamics, however the distortion in the electric field near this aperture causes the anode itself to act as a negative transverse lens. %TODO reference
Additionally, the longitudinal electric field strength sharply decreases near the anode.
As the front of the pulse sees this change before the back, this changing field also acts as a pulse compression element.

@@

To model the radial action (negative transverse lensing), we can expand the radial force $F_r$ for electrons that are a distance $r$ radially outward from the center of the pulse,
\begin{equation}
  F_r(r,z^{\prime}) \approx F_r(r,z^{\prime}) + \frac{\partial F_r}{\partial r^{\prime}} r \,\text{.}
\end{equation}
Without an analytic form for $F$, we can appeal to Gauss' law (in absence of external charge),
\begin{gather}
  \frac{\partial F_x}{\partial x^{\prime}} + \frac{\partial F_y}{\partial y^{\prime}} + \frac{\partial F_z}{\partial z^{\prime}} = 2 \frac{\partial F_{\smallT}}{\partial r^{\prime}} + \frac{\partial F_z}{\partial z^{\prime}} = 0 \\
  \Rightarrow \frac{\partial F_{\smallT}}{\partial r^{\prime}} = - \frac{1}{2} \frac{\partial F_z}{\partial z^{\prime}} \,\text{,}
\end{gather} 
to see that the transverse lens traverse lens strength $M_{\smallT}$ from the anode is simply,
\begin{equation}
  M_{\smallT} = -\frac{1}{2}\frac{\partial F_z}{\partial z^{\prime}} \, \text{.}
\end{equation}

We may choose to assume that the on-axis field is defined as a smoothed step down function
\begin{equation} \label{eq:anode_tanh}
  F_z(0,z^{\prime}) = \frac{eV}{2z^{\prime}_A} \left( 1 - \tanh \left( \frac{ z^{\prime} - z^{\prime}_A }{ z^{\prime}_A / s } \right) \right) \,\text{,}
\end{equation}
where $V$ is the accelerating potential, $z^{\prime}_A$ is the position of the anode (the cathode assumed to be at $z^{\prime} = 0$) and $s$ is a constant quantifying the ``sharpness'' of the fall-off of the electric field.
Indeed, this form is analogous to the super-Gaussian envelope (\ref{eq:reg_of_influence}), however it is open ended on the cathode side, which is necessary for the electrons to be accelerated away from the photocathode.
Given this form the ``lensing'' strengths are then
\begin{gather}
  M_{\smallT} = -\frac{eVs}{4z^{\prime 2}_A} \operatorname{sech}^2 \left( \frac{z^{\prime} - z^{\prime}_A }{ z^{\prime}_A / s } \right) \\
  M_z = \frac{eVs}{2z^{\prime 2}_A} \operatorname{sech}^2 \left( \frac{z^{\prime} - z^{\prime}_A }{ z^{\prime}_A / s } \right) \, \text{.}
\end{gather}
As with the RF cavity, one needs to include the on-axis force (\ref{eq:anode_tanh}) in the overall pulse propagation kinematics.

\begin{figure}
  \centerline{
    \subfloat[][]{
      \label{fig:field_on_axis}
      \begin{tikzpicture}
        \input{onaxis}
      \end{tikzpicture}
    }
    \subfloat[][]{
      \label{fig:tanh_sharpness}
      \input{sharpness}
    }
  }
  \caption[An example of a tanh form acceleration region for three different ``sharpness'' values]{
    An example of a tanh form acceleration region (overall length 6.35mm) for three different ``sharpness'' values.
    The colored electric fields in figure \protect\subref{fig:field_on_axis} correspond to the pulse width (solid) and length (dashed) in figure \protect\subref{fig:tanh_sharpness}.
    This form is compared to FEM simulated electric field data in \ref{fig:field_on_axis_fem}.
  }
  \label{fig:gun-sharpness}
\end{figure}

### 2013-04-12 inc/hardware/introduction.tex
massive spellchecking

It is common in the DTEM field to modify an existing transmission electron microscope column, adapting it for laser-stimulated electron generation.
For the reasons covered in Section \ref{sec:childs_law}, the prototype UEM at UIC is being built to accomodate electron pulses with a large transverse size.
To satisfy this restriction, it has been designed and built from parts either fabricated in-house or from commercially available sources, both for the ease of prototyping inherent in using replacable parts and to accomodate the physical limitations that our choice of a large beam width have imposed on the standard electron microscope column components.

>>>>

It is common in the DTEM field to modify an existing transmission electron microscope column, adapting it for laser-stimulated electron generation.
For the reasons covered in Section \ref{sec:childs_law}, the prototype UEM at UIC is being built to accommodate electron pulses with a large transverse size.
To satisfy this restriction, it has been designed and built from parts either fabricated in-house or from commercially available sources, both for the ease of prototyping inherent in using replaceable parts and to accommodate the physical limitations that our choice of a large beam width have imposed on the standard electron microscope column components.
